The dictionary for characters of smooth group schemes

### 2016-05-20 followup.tex
Made the connection to Lusztig, in the introduction.

Next, we broaden our scope further to encompass smooth group schemes $G$ over $\Fq$ that are not necessarily commutative.
In this paper, we do not consider Lusztig's geometrization for characters of representations of connected, reductive groups $G(k)$
using character sheaves \cite{lusztig:85a}*{Def.~2.10}.  Instead, we focus on the group of $1$-dimensional characters
$G(k)^*$, assuming that $G$ is smooth, but not that it is connected, reductive or commutative. \todo{Is there a relationship with Lusztig's character sheaves that we can easily summarize?}
The category $\CS(G)$ has a straightforward generalization to this case, but again
there are more character sheaves than there are characters, as pointed out by Kamgarpour \cite{kamgarpour:09a}*{(1.1)}.
We define a category $\CCS(G)$ and a forgetful functor to $\CS(G)$ so that $\TrFrob{G} : \CCSiso{G} \to G\ab(k)^*$
is an isomorphism.  
Since $G\ab(k)^*$ surjects onto $G(k)^*$, it follows that for each character $\chi \in G(k)^*$ there is a commutative
character sheaf $\cs{L}$ on $G$ with $\TrFrob{G}(\cs{L}) = \chi$. Moreover, we find that pullback along the quotient $q : G \to G\ab$
defines an equivalence of categories $\CCS(G\ab) \to \CCS(G)$.  Note that the functor $\CCS(G) \to \CS(G)$ is not
essentially surjective, missing the kinds of linear character sheaves highlighted by Kamgarpour.

Finally, we use the category $\CCS(G)$ to give a geometric description of types for supercuspidal representations of connected reductive groups over $p$-adic fields fields.
In this way, we provide all of the ingredients needed to parametrize supercuspidal representations of arbitrary depth in the same category:
virtual Weil perverse sheaves on group schemes over finite fields.

>>>>

Next, we broaden our scope further to encompass smooth group schemes $G$ over $\Fq$ that are not necessarily commutative.
We assume $G$ is smooth, but not that it is connected, reductive or commutative. 
The category $\CS(G)$ has a straightforward generalization to this case, but again
there are more character sheaves than there are characters, as pointed out by Kamgarpour \cite{kamgarpour:09a}*{(1.1)}.
We define a category $\CCS(G)$ and a forgetful functor to $\CS(G)$ so that $\TrFrob{G} : \CCSiso{G} \to G\ab(k)^*$
is an isomorphism.  
Since $G\ab(k)^*$ surjects onto $G(k)^*$, it follows that for each character $\chi \in G(k)^*$ there is a commutative
character sheaf $\cs{L}$ on $G$ with $\TrFrob{G}(\cs{L}) = \chi$. Moreover, we find that pullback along the quotient $q : G \to G\ab$
defines an equivalence of categories $\CCS(G\ab) \to \CCS(G)$.  Note that the functor $\CCS(G) \to \CS(G)$ is not
essentially surjective, missing the kinds of linear character sheaves highlighted by Kamgarpour.
%

In order to further justify referring to objects in $\CCS(G)$ as commutative character sheaves,
suppose for the moment that $G$ is a connected, reductive algebraic group over $\Fq$.
In this case, every object in $\CCS(G)$ is a Frobenius-stable character sheaf on $G$ in the sense of \cite{lusztig:85a}*{Def.~2.10}.
Moreover, if $A$ is a character sheaf on $G$ in this sense, and if the characteristic function of $A$ is a character of $G(k)$, then the dictionary determines an object in $\CCS(G)$ from $A$.
These two rules determine an injection from $\CCSiso{G}$ to isomorphism classes of Frobenius-stable character sheaves on $G$.
Accordingly, we may refer to character sheaves on $G$ that arise in this manner as commutative character sheaves.
Of course, such sheaves represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups.

As an application, we use the category $\CCS(G)$ to give a geometric description of types for supercuspidal representations of connected reductive groups over $p$-adic fields fields.
In this way, we provide all of the ingredients needed to parametrize supercuspidal representations of arbitrary depth in the same category:
virtual Weil perverse sheaves on group schemes over finite fields.
